Joining a master's program is challenging but rewarding work. In these two years, I have learned a lot, not only from an academic point of view but also about personal development, and this thesis is the culmination of all this effort.\\

First of all, I would like to thank Unity Technologies Finland for giving me the opportunity of joining such an amazing company, especially the Advertiser Public APIs team for making me part of the team from day one.\\

I also would like to thank my company advisor Teemu Sidoroff for helping me with this project unselfishly. In that regard, I would like also to thank my supervisor, Prof. Hong-Linh Truong, for his valuable feedback and continuous support.\\

I also think it is important to mention my utmost gratitude to the public institutions that participate in this Master's degree: EIT Digital, Aalto University, and the Technical University of Madrid. The existence of these institutions makes it possible for people with not so privileged backgrounds to strive for better opportunities.\\

Also, I would like to express my gratitude to all my friends here in Finland, without them life on campus won't be the same. In especial to Unna and to my flatmate and friend Stefano, for all the good moments lived here.\\

There is also a special place for my lifelong friends, the ones that had helped me to become the person that I am today: Rafa, Alba, Ángel, Alejandro Grillo, Reina, Alejandro Pérez, and Jorge. \textit{¡Muchas gracias!}\\

Last but not least, I would like to thank my family for their love and support during all this time and for teaching me how to be the best version of myself. \textit{¡Les quiero!}\\

\vspace{2cm}
Otaniemi, February 28, 2022

\vspace{5mm}
{\hfill Cristian M.\ Abrante Dorta \hspace{1cm}}